---
title: "Lab 0: Getting started"
date: today
format: html
embed-resources: true
dpi: 300
editor: visual
editor_options: 
  chunk_output_type: console
---

Note: We do not meet for labs this week.

## Reading

Read the article on the [stereotype threat](https://dynamicecology.wordpress.com/2014/04/28/stereotype-threat-a-summary-of-the-problem/).

## R and RStudio

Download and install [R](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/) on whatever computer you would like to work on. If you are having trouble installing R or RStudio, please Google or talk to GSIs.

## swirl

R package [swirl](https://swirlstats.com/) teaches you R programming and data science interactively, at your own pace, and right in the R console! To install it, please type the following in your R console:

```{r}
#| eval: false
install.packages('swirl')
```

To use it, first load the swirl package/library.

```{r}
library(swirl)
```

Follow all prompts. When asked which course to install, choose 1: R Programming. Please complete the following tutorials: 1. basic building blocks, 3. sequence of numbers, and 4. vectors.

If you run into any problems, please post questions on Piazza or contact GSIs.
